---
title: "methods_document"
author: "aj_mitchell"
date: "March 25, 2019"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyselect)
library(ggplot2)
library(broom)
library(dplyr)
library(corrplot)
library(kableExtra)
library(knitr)
library(Hmisc)
library(infer)
library(plotly) 
library(skimr)
library(stringr)
library(reshape2)
library(som)
library(readxl)
library(manipulate)
library(lavaan)
library(semPlot)
library(FactoMineR)
library(factoextra)
library(readxl)
library(formattable)
library(DT)
library(xtable)
```

The purpose of this document is to outline of the methods used to contruct composite variables from the raw behaviors collected form the Human Intruder Task. The data include the **Stare, Familiar Food Offer, and Novel Object** epochs and a total of 37 behaviors were included in the analysis. 

Below is a the first few rows of the normalized, raw data. Notice that the descriptive variables such as animal ID, interval time, etc have been removed in order to calculate correlations.

```{r loading the data, echo=FALSE, warning=FALSE, message=FALSE}
znormed_ffostare_v1 <- read_excel("znormed_ffostare_v1.xlsx")
#skim(znormed_ffostare_v1)

selected_norms_ffostare_v1 <- znormed_ffostare_v1 %>%
  select(-Observations, - ResultContainers, - Intervals, - Zno_sec_behav_ffosta)
         
#glimpse(selected_norms_ffostare_v1)         
```

Below is the correlation output for the data. 

```{r, echo=FALSE}
corrnorm_selected_ffostare_v1 <- cor(selected_norms_ffostare_v1)   
melted_corrnorm_selected_ffostare_v1 <- melt(corrnorm_selected_ffostare_v1)


ggplot(melted_corrnorm_selected_ffostare_v1, aes(x=Var2, y=Var1, fill=value)) +
  ggtitle("Combined Behavioral Correlations") +
  geom_tile() +
  scale_fill_gradient(low = "dark blue", high = "yellow") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1))


melted_corrnorm_selected_ffostare_v1_reduced <- melted_corrnorm_selected_ffostare_v1[order(melted_corrnorm_selected_ffostare_v1$value, decreasing = TRUE),] %>%
  filter(value <= .99)

#kable(melted_corrnorm_selected_ffostare_v1_reduced) %>%
  #kable_styling(bootstrap_options = c("hover", "condensed", "striped")) %>% 
  #scroll_box(width = "1000px", height = "400px")

as.datatable(formattable(melted_corrnorm_selected_ffostare_v1_reduced,
                         align = c("l", "l")))
```

From correlational values above were used to investigate the relationships amongst the behaviors. Specifically, how behaviors cluster together. To do this, an empirical approach was chosen that used community detection algorithm to determin which behaviors were clustering together. 

The output of the community detection is outline below. 4 communities were detected by this empirical process. These communities will now be considered **composite behaviors** (thus 4 composite behaviors emerged from this analysis) which we will investigate diet differences on. 

One thing I want to do is reduce the size of **Composite 1**, as it contains too many variables to accurately define a latent behavioral trait. PCA and SEM modeling was used to investigated the strength of these composite groupings; those figures are at the end of this document.   

```{r creating the composite scores, echo=FALSE}
selected_norms_ffostare_v1$comp_1 <- selected_norms_ffostare_v1$Zstationary_middle_percent_butters + selected_norms_ffostare_v1$Zlocomotion_percent_butters + selected_norms_ffostare_v1$Zhanging_behaviors_butters + selected_norms_ffostare_v1$Ztactile_exploration_butters + selected_norms_ffostare_v1$Zmo_manip_apple_butters + selected_norms_ffostare_v1$Zstation_fr_ffostare + selected_norms_ffostare_v1$Zstation_mid_ffosta + selected_norms_ffostare_v1$Zlocomote_ffosta + selected_norms_ffostare_v1$Zmovement_ffosta + selected_norms_ffostare_v1$Ztac_expl_ffosta + selected_norms_ffostare_v1$Zstereo_ffosta + selected_norms_ffostare_v1$Zteethgrind_ffosta + selected_norms_ffostare_v1$Zlipsmack_ffosta + selected_norms_ffostare_v1$Ztouch_app_ffosta + selected_norms_ffostare_v1$Zmouth_app_ffosta + selected_norms_ffostare_v1$Zmanip_app_ffosta + selected_norms_ffostare_v1$Zeat_app_ffosta + selected_norms_ffostare_v1$Znonvigi_ffosta + selected_norms_ffostare_v1$Zdir_eye_contact_ffosta
  
selected_norms_ffostare_v1$comp_2 <- selected_norms_ffostare_v1$ZStationary_back_butters + selected_norms_ffostare_v1$Zstereotypy_butters + selected_norms_ffostare_v1$Zvigilant_percent_butters + selected_norms_ffostare_v1$Zstation_back_ffostare + selected_norms_ffostare_v1$Zself_gro_ffosta + selected_norms_ffostare_v1$Zthreat_stranger_ffosta + selected_norms_ffostare_v1$Zfreeze_back_ffosta 
  
selected_norms_ffostare_v1$comp_3 <- selected_norms_ffostare_v1$Zstationary_front_percent_butters + selected_norms_ffostare_v1$Zmovement_percent_butters + selected_norms_ffostare_v1$Ztouch_butters_percent + selected_norms_ffostare_v1$Zcrouching_butters + selected_norms_ffostare_v1$Znonvigilant_percent_butters + selected_norms_ffostare_v1$Zcrouching_ffosta + selected_norms_ffostare_v1$Zvigi_ffosta + selected_norms_ffostare_v1$Zno_response_ffosta
  
selected_norms_ffostare_v1$comp_4 <- selected_norms_ffostare_v1$Zself_groom_percent_butters + selected_norms_ffostare_v1$Zmouth_butters_percent + selected_norms_ffostare_v1$Zoral_exploration_butters 
```


```{r no response groups, echo=FALSE, warning=FALSE, message=FALSE}
#took two variables from composite 2 and add them to composite 3. 
selected_norms_ffostare_v1$comp_2.2 <- selected_norms_ffostare_v1$Zstereotypy_butters + selected_norms_ffostare_v1$Zstation_back_ffostare + selected_norms_ffostare_v1$Zself_gro_ffosta + selected_norms_ffostare_v1$Zthreat_stranger_ffosta + selected_norms_ffostare_v1$Zfreeze_back_ffosta


selected_norms_ffostare_v1$comp_3.2 <- selected_norms_ffostare_v1$Zstationary_front_percent_butters + selected_norms_ffostare_v1$Zmovement_percent_butters + selected_norms_ffostare_v1$Ztouch_butters_percent + selected_norms_ffostare_v1$Zcrouching_butters + selected_norms_ffostare_v1$Znonvigilant_percent_butters + selected_norms_ffostare_v1$Zcrouching_ffosta + selected_norms_ffostare_v1$Zvigi_ffosta + selected_norms_ffostare_v1$Zno_response_ffosta + selected_norms_ffostare_v1$ZStationary_back_butters + selected_norms_ffostare_v1$Zvigilant_percent_butters

#skim(selected_norms_ffostare_v1)

#write.csv(selected_norms_ffostare_v1, "selected_norms_composites_demgraf_v2.csv")
```
The output below represents the composite scores for the individual animals. 

Composite scores were created by taking the value of each individual behavior from the output of community detection. Below represent the individual scores for each animal and their respective categorical groupings.

Need to have a 'what you are looking at here explanation'

```{r inserting demographic infomation, echo=FALSE}
selected_norms_composites_demgraf_v1.2 <- read.csv("selected_norms_composites_demgraf_v2.csv")
#View(selected_norms_composites_demgraf_v1.2)

composite_scores_withgroups <- selected_norms_composites_demgraf_v1.2[order(selected_norms_composites_demgraf_v1.2$initial_diet),]  %>%
  select(Observations, sex, initial_diet, new_diet, comp_1, comp_2, comp_3, comp_4, comp_3.2, comp_2.2) 

composite_scores_withgroups$initial_diet <- as.factor(composite_scores_withgroups$initial_diet)
composite_scores_withgroups$new_diet <- as.factor(composite_scores_withgroups$new_diet)
composite_scores_withgroups$sex <- as.factor(composite_scores_withgroups$sex)

#glimpse(composite_scores_withgroups)

#(composite_scores_withgroups)

#kable(composite_scores_withgroups) %>%
 # kable_styling(bootstrap_options = c("hover", "condensed", "striped"),
                #full_width = F,
                #position = "center") %>%
  #add_header_above(c(" " = 2, "Diet Groups" = 2, "Composite Scores" = 6))

```

```{r filtering out individuals with postnatal diet group 2, echo=FALSE}
matdiet_filtered <- composite_scores_withgroups %>%
  filter(!new_diet == 2)

matdiet_filtered_v2 <- composite_scores_withgroups %>%
  filter(!new_diet == 2)

#View(matdiet_filtered_v2)
```


##Wilcoxon Tests on effects of Maternal Diet, Sex, and Postnatal Diet##

Below are the Pvalues for each of the composite groups. These values were calculated using the Wilcoxon rank sum test after failing the normality test. Only Composite Variable 1 and Composite Variable 2 displayed a significant effect of diet group.

These data are void of subjects with a postnatal HFD diet in order to only look at the effects of maternal diet on temperament. 

```{r t test for effects of maternal diet, echo=FALSE, warning = FALSE, mesage = FALSE}
matdiet_filtered_wiltest_comp1 <- wilcox.test(matdiet_filtered$comp_1~matdiet_filtered$initial_diet)
matdiet_filtered_wiltest_comp2 <- wilcox.test(matdiet_filtered$comp_2~matdiet_filtered$initial_diet)
matdiet_filtered_wiltest_comp3 <- wilcox.test(matdiet_filtered$comp_3~matdiet_filtered$initial_diet)
matdiet_filtered_wiltest_comp4 <- wilcox.test(matdiet_filtered$comp_4~matdiet_filtered$initial_diet)
matdiet_filtered_wiltest_comp3.2 <- wilcox.test(matdiet_filtered_v2$comp_3.2~matdiet_filtered$initial_diet)
matdiet_filtered_wiltest_comp2.2 <- wilcox.test(matdiet_filtered_v2$comp_2.2~matdiet_filtered$initial_diet)
matdiet_filtered_wiltest_comp1_check <- wilcox.test(matdiet_filtered_v2$comp_1~matdiet_filtered$initial_diet)



matdiet_pvals <- c(matdiet_filtered_wiltest_comp1$p.value, matdiet_filtered_wiltest_comp2$p.value, matdiet_filtered_wiltest_comp2.2$p.value, matdiet_filtered_wiltest_comp3$p.value, matdiet_filtered_wiltest_comp3.2$p.value, matdiet_filtered_wiltest_comp4$p.value)
composite_frame_matdietpval <- c("Composite 1 P-value",
                                 "Composite 2 P-value",
                                 "Composite 2.2 P-value",
                                 "Composite 3 P-value",
                                 "Composite 3.2 P-value",
                                 "Composite 4 P-value")

matdiet_composite_difference <- data.frame(composite_frame_matdietpval, matdiet_pvals)

#View(matdiet_composite_difference)

#kable(matdiet_composite_difference, format = "html", align=rep('l', 5)) %>%
  #kable_styling(bootstrap_options = c("condensed", "striped"))


bold_pvals <- formatter("span",
                        style = x ~ style("font-weight" = ifelse(x<.05, "bold", NA)))

#formattable(matdiet_composite_difference, list(
  #matdiet_pvals = bold_pvals
#))

as.datatable(formattable(matdiet_composite_difference,
                         align = c("l", "l"),
                         list(matdiet_pvals = bold_pvals)
                         ))

#xtab1 <- xtable(summary(matdiet_filtered_wiltest_comp2))
#View(xtab1)

#make a data table here!
```

Below are scatterplots and bar plots of individual scores relating to the significant composite behaviors. Bar plots can provide insight into specific cohort differences whereas the scatterplots let you see the visualize the overall difference in performance. Only the results of the maternal diet were visualized. 

```{r visulizations of significant composites for maternal diet, echo=FALSE, warning = FALSE}
ggcomp1 <- ggplot(matdiet_filtered, aes(x=Observations, y=comp_1, color=initial_diet, fill=initial_diet)) +
  geom_bar(stat = "identity", width = 20, position = position_dodge())

ggcomp2 <- ggplot(matdiet_filtered, aes(x=Observations, y=comp_2, color=initial_diet, fill=initial_diet)) +
  geom_bar(stat = "identity", width = 20, position = position_dodge())

ggcomp2.2 <- ggplot(matdiet_filtered_v2, aes(x=Observations, y=comp_2.2, color=initial_diet, fill=initial_diet)) +
  geom_bar(stat = "identity", width = 20, position = position_dodge())

dotplotly_comp2 <- ggplot(matdiet_filtered, aes(x=Observations, y=comp_2, color=initial_diet, fill=initial_diet)) +
  geom_point(stat = "identity") + 
  geom_smooth(method = "lm", se = FALSE)

dotplotly_comp2.2 <- ggplot(matdiet_filtered_v2, aes(x=Observations, y=comp_2.2, color=initial_diet, fill=initial_diet)) +
  geom_point(stat = "identity") + 
  geom_smooth(method = "lm", se = FALSE)

ggcompl2_ly <- ggplotly(ggcomp2)
ggcompl2_ly

ggdotcomp2_ly <- ggplotly(dotplotly_comp2)
ggdotcomp2_ly

ggcompl2.2_ly <- ggplotly(ggcomp2.2)
ggcompl2.2_ly

ggdotcomp2.2_ly <- ggplotly(dotplotly_comp2.2)
ggdotcomp2.2_ly


dotplotly_comp1 <- ggplot(matdiet_filtered, aes(x=Observations, y=comp_1, color=initial_diet, fill=initial_diet)) +
  geom_point(stat = "identity") + 
  geom_smooth(method = "lm", se = FALSE)

ggcompl1_ly <- ggplotly(ggcomp1)

ggcompl1_ly

ggdotcomp1_ly <- ggplotly(dotplotly_comp1)

ggdotcomp1_ly
```

The table below describes differences observed based on sex. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
matdiet_sex_wiltest_comp1 <- wilcox.test(matdiet_filtered$comp_1~matdiet_filtered$sex)
matdiet_sex_wiltest_comp2 <- wilcox.test(matdiet_filtered$comp_2~matdiet_filtered$sex)
matdiet_sex_wiltest_comp3 <- wilcox.test(matdiet_filtered$comp_3~matdiet_filtered$sex)
matdiet_sex_wiltest_comp4 <- wilcox.test(matdiet_filtered$comp_4~matdiet_filtered$sex)
matdiet_sex_wiltest_comp3.2 <- wilcox.test(matdiet_filtered_v2$comp_3.2~matdiet_filtered$sex)
matdiet_sex_wiltest_comp2.2 <- wilcox.test(matdiet_filtered_v2$comp_2.2~matdiet_filtered$sex)

matdiet_sex_wiltest_comp3.2$p.value

matdiet_sex_pvals <- c(matdiet_sex_wiltest_comp1$p.value, matdiet_sex_wiltest_comp2$p.value, matdiet_sex_wiltest_comp2.2$p.value, matdiet_sex_wiltest_comp3$p.value, matdiet_sex_wiltest_comp3.2$p.value, matdiet_sex_wiltest_comp4$p.value)
composite_sexframe_matdietpval <- c("Composite 1 P-value ",
                                 "Composite 2 P-value",
                                 "Composite 2.2 P-value",
                                 "Composite 3 P-value",
                                 "Composite 3.2 P-value",
                                 "Composite 4 P-value")

matdiet_composite_difference_sex <- data.frame(composite_sexframe_matdietpval, matdiet_sex_pvals)

as.datatable(formattable(matdiet_composite_difference_sex,
                         align = c("l", "l")
                         ))
```

The table below describes the effect of postnatal diet only. Only subjects with prenatal HFD and postnatal HFD exposure were compared to pre/postnatal controls. 

```{r filtering out individuals with materal diet group 1, echo=FALSE, warning=FALSE, message=FALSE}
#for shits and giggles, here i'm filitering down to subjects that had both matdiet2 and post2 vs matdiet1 and matdiet1

#glimpse(composite_scores_withgroups)



newdiet_filtered <- composite_scores_withgroups %>%
  filter(Observations %in% c(30586, 30637, 30639, 30726, 31266, 30155, 30181, 30397, 30398, 31177, 31347, 31347, 31479, 31480, 31700))

newdiet_differences_wiltest_comp1 <- wilcox.test(newdiet_filtered$comp_1~newdiet_filtered$new_diet)
newdiet_differences_wiltest_comp2 <- wilcox.test(newdiet_filtered$comp_2~newdiet_filtered$new_diet)
newdiet_differences_wiltest_comp2.2 <- wilcox.test(newdiet_filtered$comp_2.2~newdiet_filtered$new_diet)
newdiet_differences_wiltest_comp3 <- wilcox.test(newdiet_filtered$comp_3~newdiet_filtered$new_diet)
newdiet_differences_wiltest_comp3.2 <- wilcox.test(newdiet_filtered$comp_3.2~newdiet_filtered$new_diet)
newdiet_differences_wiltest_comp4 <- wilcox.test(newdiet_filtered$comp_4~newdiet_filtered$new_diet)

newdiet_differences_wiltest_comp4$p.value

newdiet_pvals <- c(newdiet_differences_wiltest_comp1$p.value, newdiet_differences_wiltest_comp2$p.value, newdiet_differences_wiltest_comp2.2$p.value, newdiet_differences_wiltest_comp3$p.value, newdiet_differences_wiltest_comp3.2$p.value, newdiet_differences_wiltest_comp4$p.value)
newdiet_titles <- c("Composite 1 P-value ",
                    "Composite 2 P-value",
                    "Composite 2.2 P-value",
                    "Composite 3 P-value",
                    "Composite 3.2 P-value",
                    "Composite 4 P-value")
newdiet_pvals_df <- data.frame(newdiet_titles, newdiet_pvals)
as.datatable(formattable(newdiet_pvals_df, 
                         align = c("l", "l")
                         ))
#View(newdiet_pvals_df)
```

##PCAs and Structural Models##

Below is the pca from the composite behavior groups. Additionally, structural equation modeling has been used to look at the strength of the groupings. 


```{r creating individual composites for pca and sem, echo=FALSE, warning=FALSE, message=TRUE}
comp1_indi <- selected_norms_ffostare_v1 %>%
  select(Zstationary_middle_percent_butters, Zlocomotion_percent_butters, Zhanging_behaviors_butters, Ztactile_exploration_butters, Zmo_manip_apple_butters, Zstation_fr_ffostare,  Zstation_mid_ffosta, Zlocomote_ffosta, Zmovement_ffosta, Ztac_expl_ffosta,  Zstereo_ffosta, Zteethgrind_ffosta, Zlipsmack_ffosta, Ztouch_app_ffosta, Zmouth_app_ffosta, Zmanip_app_ffosta, Zeat_app_ffosta, Znonvigi_ffosta, Zdir_eye_contact_ffosta)

comp2_indi <- selected_norms_ffostare_v1 %>%
  select(ZStationary_back_butters, Zstereotypy_butters, Zvigilant_percent_butters, Zstation_back_ffostare, Zself_gro_ffosta, Zthreat_stranger_ffosta, Zfreeze_back_ffosta)

comp2.2_indi <- selected_norms_ffostare_v1 %>%
  select(Zstereotypy_butters, Zstation_back_ffostare, Zself_gro_ffosta, Zthreat_stranger_ffosta, Zfreeze_back_ffosta)

comp3_indi <- selected_norms_ffostare_v1 %>%
  select(Zstationary_front_percent_butters, Zmovement_percent_butters, Ztouch_butters_percent, Zcrouching_butters, Znonvigilant_percent_butters, Zcrouching_ffosta, Zvigi_ffosta, Zno_response_ffosta)

comp3.2_indi <- selected_norms_ffostare_v1 %>%
  select(ZStationary_back_butters, Zstationary_front_percent_butters, Zmovement_percent_butters, Zvigilant_percent_butters, Ztouch_butters_percent, Zcrouching_butters, Znonvigilant_percent_butters, Zcrouching_ffosta, Zvigi_ffosta, Zno_response_ffosta)

comp4_indi <- selected_norms_ffostare_v1 %>%
  select(Zself_groom_percent_butters, Zmouth_butters_percent, Zoral_exploration_butters)

```

**The text box will describe the scree plot output below.**

```{r, echo=FALSE, warning = FALSE, message = FALSE}
princi_comp1 <- prcomp(comp1_indi)
summary(princi_comp1)
#princi_comp1$sdev
princ1_ploty  <- ggplotly(fviz_eig(princi_comp1, main = "variance explained: components of comp_1"))

#xtable(princi_comp1)

princ1_ploty

princi_comp2 <- prcomp(comp2_indi)
summary(princi_comp2)
#fviz_eig(princi_comp2, main = 'variance explained: components of comp_2')

princi_comp2

princ2_ploty <- ggplotly(fviz_eig(princi_comp2, main = 'variance explained: components of comp_2'))

princ2_ploty

princi_comp2.2 <- prcomp(comp2.2_indi)
summary(princi_comp2.2)
#fviz_eig(princi_comp2.2, main = 'variance explained: components of comp_2.2')

#xtable

princ2.2_ploty <- ggplotly(fviz_eig(princi_comp2.2, main = 'variance explained: components of comp_2.2'))

princ2.2_ploty

princi_comp3 <- prcomp(comp3_indi)
summary(princi_comp3)
#fviz_eig(princi_comp3, main = "variance explained: components of comp_3")

#xtable

princ3_ploty <- ggplotly(fviz_eig(princi_comp3, main = 'variance explained: components of comp_3'))

princ3_ploty

princi_comp3.2 <- prcomp(comp3.2_indi)
summary(princi_comp3.2)
#fviz_eig(princi_comp3.2, main = 'variance explained: components of comp_3.2')

#xtable

princ3.2_ploty <- ggplotly(fviz_eig(princi_comp3.2, main = 'variance explained: components of comp_3.2'))

princ3.2_ploty

princi_comp4 <- prcomp(comp4_indi)
summary(princi_comp4)
#fviz_eig(princi_comp4, main = "variance explained: components of comp_4")

#xtable

princ4_ploty <- ggplotly(fviz_eig(princi_comp4, main = 'variance explained: components of comp_4'))

princ4_ploty
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#need to add visualizations here
selected_behaviors_latemods <- selected_norms_ffostare_v1 %>%
  select(- comp_1, - comp_2, - comp_3, - comp_4, -comp_2.2, -comp_3.2)

SEM_comp1 <- 'latemod_comp1 =~ Zstationary_middle_percent_butters + Zlocomotion_percent_butters + Zhanging_behaviors_butters + Ztactile_exploration_butters + Zmo_manip_apple_butters + Zstation_fr_ffostare + Zstation_mid_ffosta + Zlocomote_ffosta + Zmovement_ffosta + Ztac_expl_ffosta + Zstereo_ffosta + Zteethgrind_ffosta + Zlipsmack_ffosta + Ztouch_app_ffosta + Zmouth_app_ffosta + Zmanip_app_ffosta + Zeat_app_ffosta + Znonvigi_ffosta + Zdir_eye_contact_ffosta'

SEM_comp1_fit <- cfa(model = SEM_comp1, estimator = "MLR", data = selected_behaviors_latemods)
summary(SEM_comp1_fit, standardize = TRUE, fit.measures = TRUE)  

SEM_comp1_fit

semPaths(SEM_comp1_fit,
         layout = "tree",
         color = "gray",
         whatLabels = "std",
         edge.color = "black",
         what = "std", 
         rotation = 2,
         edge.label.cex = 1.25, 
         nCharNodes = 8, 
         sizeLat = 10, 
         sizeMan = 10, 
         title = TRUE)


SEM_comp2 <- 'latemod_comp2 =~ ZStationary_back_butters + Zstereotypy_butters + Zvigilant_percent_butters + Zstation_back_ffostare + Zself_gro_ffosta + Zthreat_stranger_ffosta + Zfreeze_back_ffosta'

SEM_comp2_fit <- cfa(model = SEM_comp2, estimator = "MLR", data = selected_behaviors_latemods)
summary(SEM_comp2_fit, standardize = TRUE, fit.measures = TRUE)
SEM_comp2_table <- parTable(SEM_comp2_fit)

SEM_comp2_fit

semPaths(SEM_comp2_fit,
         layout = "tree",
         color = "gray",
         whatLabels = "std",
         edge.color = "black",
         what = "std", 
         rotation = 2,
         edge.label.cex = 1.25, 
         nCharNodes = 8, 
         sizeLat = 10, 
         sizeMan = 10, 
         title = TRUE)

#as.datatable(formattable(SEM_comp2_fit,
                         #align = c("l", "l", "l", "l", "l", "l", "l", "l", "l", "l", "l", "l", "l", "l", "l")
                         #))

SEM_comp2.2 <- 'latemod_comp2 =~ Zstereotypy_butters + Zstation_back_ffostare + Zself_gro_ffosta + Zthreat_stranger_ffosta + Zfreeze_back_ffosta'

SEM_comp2.2_fit <- cfa(model = SEM_comp2.2, estimator = "MLR", data = selected_behaviors_latemods)
summary(SEM_comp2_fit, standardize = TRUE, fit.measures = TRUE)
SEM_comp2.2_table <- parTable(SEM_comp2.2_fit)

SEM_comp2.2_fit
#note that we get rid of the negative loadings with this model

semPaths(SEM_comp2.2_fit,
         layout = "tree",
         color = "gray",
         whatLabels = "std",
         edge.color = "black",
         what = "std", 
         rotation = 2,
         edge.label.cex = 1.25, 
         nCharNodes = 8, 
         sizeLat = 10, 
         sizeMan = 10, 
         title = TRUE)
  
SEM_comp3 <- 'latemod_comp3 =~ Zstationary_front_percent_butters + Zmovement_percent_butters + Ztouch_butters_percent + Zcrouching_butters + Znonvigilant_percent_butters + Zcrouching_ffosta + Zvigi_ffosta + Zno_response_ffosta'

SEM_comp3_fit <- cfa(model = SEM_comp3, estimator = "MLR", data = selected_behaviors_latemods)
summary(SEM_comp3_fit, standardize = TRUE, fit.measures = TRUE)

SEM_comp3.2 <- 'latemod_comp3.2 =~ Zstationary_front_percent_butters + ZStationary_back_butters + Zmovement_percent_butters + Ztouch_butters_percent + Zvigilant_percent_butters + Zcrouching_butters + Znonvigilant_percent_butters + Zcrouching_ffosta + Zvigi_ffosta + Zno_response_ffosta'

SEM_comp3.2_fit <- cfa(model = SEM_comp3.2, estimator = "MLR", data = selected_behaviors_latemods)
summary(SEM_comp3_fit, standardize = TRUE, fit.measures = TRUE)
  
SEM_comp4 <- 'latemod_comp4 =~ Zself_groom_percent_butters + Zmouth_butters_percent + Zoral_exploration_butters'

SEM_comp4_fit <- cfa(model = SEM_comp4, estimator = "MLR", data = selected_behaviors_latemods)
summary(SEM_comp4_fit, standardize = TRUE, fit.measures = TRUE)


```