---
title: "new_visuals"
author: "aj_mitchell"
date: "April 23, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyselect)
library(ggplot2)
library(broom)
library(dplyr)
library(corrplot)
library(kableExtra)
library(knitr)
library(Hmisc)
library(infer)
library(plotly) 
library(skimr)
library(stringr)
library(reshape2)
library(som)
library(readxl)
library(manipulate)
library(lavaan)
library(semPlot)
library(readxl)
library(formattable)
library(DT)
library(ggthemes)
library(ggcorrplot)
library(wesanderson)
library(RColorBrewer)
#library(ggthemes)
```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
##loading the new data

#structural only @ 4mo between yr1 and yr2
##did this to maximize data set - must remove significantly more animals from data when incorporating behavior

structural_yr1_yr2 <- read_excel("structural_yr1_yr2.xlsx")
#str(structural_yr1_yr2)

#behavior plus structural @ 4mo between yr1 and yr2

perc_diffs_4mo_yr2_11mo_yr2 <- read_excel("perc_diffs_4mo_yr2_11mo_yr2.xlsx")
#View(perc_diffs_4mo_yr2_11mo_yr2)

selected_perc_diffs_4mo_yr2_11mo_yr2 <- perc_diffs_4mo_yr2_11mo_yr2 %>%
  select(- subj_id, - group)

#differences in 4mo_yr1 and 11mo_yr2
##here i'm trying to look at the percent change between the 7 months and see if animals given a normal diet showed greater changes in areas associated with behaviors (i.e are there differences in percent change in areas related to the behavioral deficiets we see - is there a flatter slope in the PFC between diet groups and does their behavior reflect this?)

behav_plus_struc_4moyr1_4moyr2 <- read_excel("behav_plus_struc_4moyr1_4moyr2.xlsx")
#str(behav_plus_struc_4moyr1_4moyr2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

##testing
##select out variables (only in perc_diffs) and calculate correlations as well as pvalues and melt data
##here we are also going to start incorporating the cor.test funciton to get pvalues for Elinor
    #compare matrices to make sure they look the same - problem is i need to make my data in a different format for pvalues 

#cor_structural_yr1_yr2 <- cor(structural_yr1_yr2)

#cor_pval_structural_yr1_yr2 <- rcorr(as.matrix(structural_yr1_yr2))

#cor_structural_yr1_yr2

#cor_pval_structural_yr1_yr2$P

#melted_cor_structural_yr1_yr2_cor <- melt(cor_structural_yr1_yr2)
#melted_cor_structural_yr1_yr2_rcorr <- melt(cor_pval_structural_yr1_yr2$r)

#thresh_melted_cor_pval_structural_yr1_yr2 <- melt(cor_pval_structural_yr1_yr2$P) %>%
  #filter(value <= .05)

#gplot_thresh_melted_cor_pval_structural_yr1_yr2 <- 
  
  #ggplot(melted_cor_structural_yr1_yr2_cor, aes(x=Var2, y=Var1, fill=value)) +
  #geom_tile() +
  #scale_fill_gradientn(colours = topo.colors(10)) + 
  #theme_minimal() +
  #theme(axis.text.x = element_text(angle = 90,
   #                                vjust = 1,
    #                               size = 9,
     #                              hjust = 1,
      #                              ))

#gplot_thresh_melted_cor_pval_structural_yr1_yr2 + labs(title="Structural Relationships between Yr1 and Yr1: Correlations", x="P Value", y="P Value") 

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
#starting real analysis

####structure

cor_pval_structural_yr1_yr2 <- rcorr(as.matrix(structural_yr1_yr2))
melted_cor_structural_yr1_yr2_rcorr <- melt(cor_pval_structural_yr1_yr2$r)

#str(melted_cor_structural_yr1_yr2_rcorr)

thresh_melted_cor_pval_structural_yr1_yr2 <- melt(cor_pval_structural_yr1_yr2$P) %>%
  filter(value <= .05)

####percent differences

cor_perc_diffs_4mo_yr2_11mo_yr2 <- rcorr(as.matrix(selected_perc_diffs_4mo_yr2_11mo_yr2))
melted_cor_perc_diffs_4mo_yr2_11mo_yr2 <- melt(cor_perc_diffs_4mo_yr2_11mo_yr2$r)
removed_dups_perc_diffs <- melt(cor_perc_diffs_4mo_yr2_11mo_yr2$r) %>%
  filter(value <= 1,
         value >=.25)
thresh_melted_pvals_melted_cor_perc_diffs_4mo_yr2_11mo_yr2 <- melt(cor_perc_diffs_4mo_yr2_11mo_yr2$P) %>%
  filter(value <= .05)

#####behavior plus structure


  
cor_behav_plus_struc_4moyr1_4moyr2 <- rcorr(as.matrix(behav_plus_struc_4moyr1_4moyr2))
melted_cor_behav_plus_struc_4moyr1_4moyr2 <- melt(cor_behav_plus_struc_4moyr1_4moyr2$r)
thresh_melt_behav_struc_test4pval <- melt(cor_behav_plus_struc_4moyr1_4moyr2$r) %>%
  filter(value <= 1,
         value >= .25)
thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2 <- melt(cor_behav_plus_struc_4moyr1_4moyr2$P) %>%
  filter(value <= .05)

removed_dups_behave_plus_struc <- thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2[!duplicated(thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2$value), ]

removed_dups_behave_plus_struc <- thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2[!duplicated(thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2$value), ]

#duplicated(thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2$value) 
```

##Structure Only Visualizations##

The data below only contains information related to the **structural data**. I did this beacause it maximizes the amount of subjects we can use to look at the relationships between brain regions. 

**The table in this section contains information related to Pvalue and will not contain behaviors**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 15, fig.width = 18}

##Structure Only

#plot of correlation values of structure only
gplot_corplot_structure_corval <- ggcorrplot(cor_pval_structural_yr1_yr2$r, hc.order = TRUE, type = "lower", colors = topo.colors(3)) +  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_corplot_structure_corval + labs(title="Structural Relationships between Yr1 and Yr2: Correlations", x="Correlation Stregnth", y="Correlation Stregnth")

#plot of pvalues for structure only
gplot_corplot_structure_pval <- ggplot(thresh_melted_cor_pval_structural_yr1_yr2, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(5)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_corplot_structure_pval + labs(title="Structural Relationships between Yr1 and Yr2: Pvalue", x="Significance Stregnth", y="Significance Stregnth")


##this is all structure
datatable(formattable(thresh_melted_cor_pval_structural_yr1_yr2))
```

##4mo Year 1 and 4mo Year 2: Structure plus Behavior##

THis contains the information you requested. These data contain structural information from 4mo_yr1 and 4mo_yr2 subjects, and has their behaviors included. Due to the zeros in the data, i could not make remake the previous visual.  

The table in this section represents the significant P values. **type 'Z frontal' or 'Z FA'** to look at the specific ROIs relationships with behaviors 


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 15, fig.width = 18}

##Structure plus behavior

#plot of correlation values of structure plus behavior
##does not work bc of NaNs
#gplot_corplot_behave_struct_corval <- ggcorrplot(cor_behav_plus_struc_4moyr1_4moyr2$r, hc.order = TRUE, type = "lower", colors = topo.colors(3)) +  theme_minimal() +
  #theme(axis.text.x = element_text(angle = 90,
   #                                vjust = 1,
    #                               size = 9,
     #                              hjust = 1
      #                              ))

#gplot_corplot_behav_struct_corval + labs(title="Behavior and Structure Relationships between Yr1 and Yr2: Correlations", x="Correlation Stregnth", y="Correlation Stregnth")

##above does not work bc of NaNs
gplot_behav_plus_struc_4moyr1_4moyr2_v2 <- ggplot(melted_cor_behav_plus_struc_4moyr1_4moyr2, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(9)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    )) +
     theme(axis.text.y = element_text(margin = margin(b = .5, t=.5),
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_behav_plus_struc_4moyr1_4moyr2_v2 + labs(title="Year1 and Year2: Structure related to Behavior: Correlation Values", x="Correlation Stregnth", y="Correlation Stregnth")




#plot of pvalues for structure plus behavior
gplot_corplot_behave_structure_pval <- ggplot(thresh_melted_pvals_cor_behav_plus_struc_4moyr1_4moyr2, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(5)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_corplot_behave_structure_pval + labs(title="Year1 and Year2: Structure related to Behavior: Pvalue", x="Significance Stregnth", y="Significance Stregnth")

datatable(formattable(removed_dups_behave_plus_struc))
```

##Percent Difference during year 2 related to behavior##

The data below contain information about the percent difference as related to behavior. I took the 11mo structural values and subtracted the 4mo structural values, then divided that metric by the original, 11mo values. This provides a percent change value that I combined with behavior.

Chris stated that there is inherent error in this because you need to control for a number of factors but i thought it would be interesting to see. However, i think it may be more informative to do this differently, possibly with a regression model looking at diffferences in the slopes of particular ROIs associated with the prosocial behavior. 

The bottom table represents the significant P values. **type 'Z frontal' or 'Z FA'** so look at the specific ROIs relationships with behaviors.


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 15, fig.width = 18}
##percent differences between year 2, 4mo and 11mo 

#plot of correlation values of percent differences between year 2, 4mo and 11mo
##DOESNT WORK DUE TO NaNs
#gplot_corplot_percdiff_corval <- ggcorrplot(cor_perc_diffs_4mo_yr2_11mo_yr2$r, hc.order = TRUE, type = "lower", colors = topo.colors(3)) +
  #theme_minimal() +
  #theme(axis.text.x = element_text(angle = 90,
                                  # vjust = 1,
                                  # size = 9,
                                   #hjust = 1
                                  #  ))

#gplot_corplot_structure_corval + labs(title="Year2: Percent Differences 4mo/11mo in Structure related to Behavior: Correlations", x="Correlation Stregnth", y="Correlation Stregnth")

#######above doesnt work bc of NaNs...

gplot_corplot_percdiff_corval_v2 <- ggplot(melted_cor_perc_diffs_4mo_yr2_11mo_yr2, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(10)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    )) +
     theme(axis.text.y = element_text(margin = margin(b = .5, t=.5),
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_corplot_percdiff_corval_v2 + labs(title="Year2: Percent Differences in 4mo/11mo Structure related to Behavior: Correlation Values", x="Correlation Stregnth", y="Correlation Stregnth")

#plot of pvals values of percent differences between year 2, 4mo and 11mo
gplot_corplot_cor_percdiff_pval <- ggplot(thresh_melted_pvals_melted_cor_perc_diffs_4mo_yr2_11mo_yr2, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(5)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    )) +
   theme(axis.text.y = element_text(
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_corplot_cor_percdiff_pval + labs(title="Year2: Percent Differences in 4mo/11mo Structure related to Behavior: Pvalue", x="Significance Stregnth", y="Significance Stregnth")


datatable(formattable(thresh_melted_pvals_melted_cor_perc_diffs_4mo_yr2_11mo_yr2))
```

again, i know the composite behavior isn't included in these and i will get that together soon. Its a bit laborious beacuse a new data set has to be created to investigate each relationship. What makes it difficult is combining the two data sets in a way that preserved the data and also allows to create these visuals. I think in order to look at the relationship between 4mo_yr1_structure, 4mo_yr2_structure, and the prosocial behvaioral composite will take a different method. I'm currently trying to think about the best way to do this.  

##combining 4mo year1 and year2 (properly)##

```{r}
allcombine_4mo_v1 <- read_excel("4mo_allcombine_v1.xlsx")
View(allcombine_4mo_v1)

selected_4mo_allcombine_v1 <- allcombine_4mo_v1 %>%
  select(- subj_id, - group, - year)


corr_selected_4mo_allcombine_v1 <- rcorr(as.matrix(selected_4mo_allcombine_v1))
melted_corvals_corr_selected_4mo_allcombine_v1 <- melt(corr_selected_4mo_allcombine_v1$r)
melted_pvals_corr_selected_4mo_allcombine_v1 <- melt(corr_selected_4mo_allcombine_v1$P) %>% 
  filter(value <= .05)

```


```{r}
gplot_melted_corvals_corr_selected_4mo_allcombine_v1 <- ggplot(melted_corvals_corr_selected_4mo_allcombine_v1, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(10)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    )) +
     theme(axis.text.y = element_text(margin = margin(b = .5, t=.5),
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_melted_corvals_corr_selected_4mo_allcombine_v1 + labs(title="Year1 and Year 2 4mo Structure plus Behavior: Correlation Vals", x="Correlation Stregnth", y="Correlation Stregnth")


gplot_melted_pvals_corr_selected_4mo_allcombine_v1 <- ggplot(melted_pvals_corr_selected_4mo_allcombine_v1, aes(x=Var2, y=Var1, fill=value)) +
  geom_tile() +
  scale_fill_gradientn(colours = topo.colors(10)) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    )) +
     theme(axis.text.y = element_text(margin = margin(b = .5, t=.5),
                                   vjust = 1,
                                   size = 9,
                                   hjust = 1
                                    ))

gplot_melted_pvals_corr_selected_4mo_allcombine_v1 + labs(title="Year1 and Year 2 4mo Structure plus Behavior: P-Vals", x="Pvalue", y="Pvalue")


datatable(formattable(melted_pvals_corr_selected_4mo_allcombine_v1))
```

